### 2020-01-03 misc/solutions/baby-sols.tex
Lots of changes
Added more solutions

@@

\proof Let $A$ denote the set of all algebraic numbers and suppose, towards a contradiction, that all real numbers are algebraic. Then ${\bf R}\subset A$. But the set of real numbers is uncountable and we know from Problem 2 that $A$ is countable. The contradiction completes the proof.\slug

@@

>>>>

\def\d{\,d}

@@

\proof Let $A$ denote the set of all algebraic numbers and suppose, towards a contradiction, that all real numbers are algebraic. Then ${\bf R}\subseteq A$. But the set of real numbers is uncountable and we know from Problem 2 that $A$ is countable. The contradiction completes the proof.\slug

@@

\section CHAPTER 11. THE LEBESGUE THEORY

\proclaim 1. If $f\geq 0$ and $\int_E f\d\mu = 0$, prove that $f(x) = 0$ almost everywhere on $E$. {\it Hint:} Let $E_n$ be the subset of $E$ on which $f(x)> 1/n$. Write $A = \bigcup_{n=1}^\infty E_n$. Then $\mu(A) = 0$ if and only if $\mu(E_n) = 0$ for every $n$.

\proof First we claim that $\mu(E_n) = 0$ for every $n$. Suppose, towards a contradiction, that $\mu(E_n) > 0$ for some $n$. Then since $f(x) > 1/n$ for all $x\in E_n$, we find that
$$\int_E f\d\mu \geq \int_{E_n} f \d\mu > {\mu(E_n)\over n} > 0,$$
contradicting our hypothesis. Now since $\mu(E_n) = 0$ for all $n$, $\mu(A) \leq \sum_{n=1}^\infty \mu(E_n) = 0$. So $\mu(A) = 0$. Now we write
$$\int_E f\d\mu = \int_{E\setminus A} f\d\mu + \int_{A} f\d\mu,$$
and $f$ is equal to 0 on $E\setminus A$ by our construction of $A$.\slug

### 2020-01-03 misc/solutions/papa-sols.tex
Added more solutions

Lastly, we show that if $f$ is measurable and takes on the value $k$ at all but countably many points, then $\int_E f\,d\mu = k$ for all uncountable $E\in {\cal M}$. (If $E$ is countable then $\int_E f\,d\mu = 0$.)

\proof Let $E\in {\cal M}$ be uncountable; so $\mu(E) = 1$. Let $s$ be a simple measurable function such that $0\leq s\leq f$. Suppose that $s$ takes values $\alpha_i$ on the $n$ disjoint sets $A_i$ that cover $X$. We know that one of the $\alpha_i$, call it $\alpha_j$, is equal to a constant $k_s$ and that $A_i$ is at most countable for all $i \neq j$. So for all $i \neq j$, $A_i \cap E$ is countable and $A_j \cap E$ must be uncountable. Then we have
$$\int_E s\,d\mu = \sum_{i=1}^n \alpha_i \mu(A_i\cap E) = \alpha_j\mu(A_j\cap E) = k_s\cdot 1 = k_s,$$
where $0\leq k_s \leq k$. So we have
$$\int_E f\,d\mu = \sup \Big\{ \int_E s\,d\mu : 0 \leq s\leq f\Big\} = \sup \{k_s : 0\leq s \leq f\} = k,$$
which is what we had to show.\slug
\bye

>>>>

Lastly, we show that if $f$ is measurable and takes on the value $k$ at all but countably many points, then $\int_E f\d\mu = k$ for all uncountable $E\in {\cal M}$. (If $E$ is countable then $\int_E f\d\mu = 0$.)

\proof Let $E\in {\cal M}$ be uncountable; so $\mu(E) = 1$. Let $s$ be a simple measurable function such that $0\leq s\leq f$. Suppose that $s$ takes values $\alpha_i$ on the $n$ disjoint sets $A_i$ that cover $X$. We know that one of the $\alpha_i$, call it $\alpha_j$, is equal to a constant $k_s$ and that $A_i$ is at most countable for all $i \neq j$. So for all $i \neq j$, $A_i \cap E$ is countable and $A_j \cap E$ must be uncountable. Then we have
$$\int_E s\d\mu = \sum_{i=1}^n \alpha_i \mu(A_i\cap E) = \alpha_j\mu(A_j\cap E) = k_s\cdot 1 = k_s,$$
where $0\leq k_s \leq k$. So we have
$$\int_E f\d\mu = \sup \Big\{ \int_E s\d\mu : 0 \leq s\leq f\Big\} = \sup \{k_s : 0\leq s \leq f\} = k,$$
which is what we had to show.\slug

\proclaim 7. Suppose $f_n : X\rightarrow[0,\infty]$ is measurable for $n=1,2,3,\ldots$, $f_1\geq f_2\geq f_3\geq\cdots\geq 0$, $f_n(x)\rightarrow f(x)$ as $n\rightarrow\infty$ for every $x\in X$, and $f_1\in L^1(\mu)$. Prove that then
$$\lim_{n\rightarrow\infty} \int_X f_n \d\mu = \int_X f\d\mu$$
and show that this conclusion does {\it not} follow if the condition ``$f_1\in L^1(\mu)$'' is omitted.

\proof Consider the sequence of functions $(f_1 - f_n)$. This sequence is nonnegative, nondecreasing and for any $x\in X$, $\lim_{n\rightarrow\infty} (f_1 - f_n)(x) = f_1(x) - f(x)$. So by the monotone convergence theorem,
$$= \lim_{n\rightarrow \infty} \int_X f_1 - f_n \d\mu = \int_X f_1 - f\d\mu.$$
Since the integrals of $f_n$ are finite, we can apply Theorem 1.27 to get
$$\int_X f_1\d\mu - \lim_{n\rightarrow \infty}\int_X f_n \d\mu = \int_X f_1\d\mu -  \int_X f \d\mu,$$
which gives us what we want after subtracting $\int_X f_1 \d\mu$ (which is finite) and multiplying by $-1$.\slug

The condition $f_1\in L^1(\mu)$ is necessary. Let $I = [0,1]$ and $f_n = {1\over nx^2}$, which converges to the constant function 0. Then $\lim_{n\rightarrow \infty} \int_I f_n \d\mu = +\infty$ but $\int_I 0\d\mu = 0$.

\bye
